---
title: "Load_and_present_img"
output: rmarkdown::html_vignette
runtime: shiny
vignette: >
  %\VignetteIndexEntry{Load_and_present_img}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Stereology)
```

# Initial data loading and visualization

## Load image
```{r}
file_path <- system.file("extdata", "sponge3.jpg", package = "Stereology")
img <- load_img(file_path)
class(img)
```
## Visualize
```{r}
# Plot
p <- plot.stero(img)
p
```

## Add grid
```{r}
p <- add_grid(p)
p
```


## Example of theoretical exploration of the image.

Below, there is an example of the functions 'mat_gen()' and 'th_i_est()' being used. <br/>
First, the image file to be used is loaded onto R, then the function mat_gen() is used. This function turns the image to a matrix of 1s and 0s, which in this case represent whether the area is 'filled' by sponge or not respectively.  As we can see its a 1899 by 1266 matrix. <br/>
After using the generated matrix ('mat'), as the first argument of the th_i_ests() function, we start from pixel/entry (x=)10 and add the length(d=) 10. We then do the same for y. As a last argument in the function, we specify the trial size (trial_s) in order to generate the binomial simulations. The function then outputs a list containing: <br/>

- the part of the matrix we subsetted for,
- the probability (p) estimated using this sub-matrix,
- the average of the p_hats generated through simulations, and
- the variance of those p_hats.

```{r}
# loading the image.

# to use a PNG/JPEG/BMP image stored on your computer try:
# path <- "~/images.png"
path <- system.file('extdata/sponge3.jpg',package='Stereology')

# applying mat_gen().
mat <- mat_gen(path)

# matrix dimensions.
dim(mat)

# applying th_i_ests()
est_list <- th_i_ests(mtr = mat, x = 10, y = 10, d= 10, trial_s = 1000)
est_list

```



# Stereology

Let's try finding some points in a sponge
```{r}
ster()
```





